---
title: "Inferential Exploratory Data Analysis"
author: "Stephen Sani"
date: "April 4, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1. Loading the data
The ToothGrowt data was loaded
```{r}
data("ToothGrowth")
```


##2. Summarizing and analysing the data
The first six rows of the data was viewed
```{r}
head(ToothGrowth)
```

The summary of the ToothGrowth data was obtained
```{r}
summary(ToothGrowth)
```

The structure of the data was obtained
```{r}
str(ToothGrowth)
```

The distribution of the data was ploted by supp and dose variables
```{r}
library(ggplot2)
qplot(len, data=ToothGrowth, facets = .~supp+dose, binwidth=2)
```

##3. Confidence interval
####(a.) Confidence interval for the two "supp" levels
The dataframe was subset by the two "supp" levels "OJ" and "VC"
```{r}
supp1<-ToothGrowth[ToothGrowth$supp=="OJ", "len"]
supp2<-ToothGrowth[ToothGrowth$supp=="VC", "len"]
```

Confidence interval for the test statistic was obtained for H(null)=0
```{r}
t.test(supp1, supp2, paired = FALSE, var.equal = FALSE)$conf
```

Since the interval includes 0, we fail to reject the Null hypothesis

####(b.) Confidence interval for combinations of dose levels
The data frame was subset by the dose levels
```{r}
x1<-ToothGrowth[ToothGrowth$dose=="0.5", "len"]
x2<-ToothGrowth[ToothGrowth$dose=="1", "len"]
x3<-ToothGrowth[ToothGrowth$dose=="2", "len"]
```

Confidence interval for the test statistic between "0.5" and "1" was obtained for H(null)=0
```{r}
t.test(x1, x2, paired = FALSE, var.equal = FALSE)$conf
```

Since the interval does not include 0, We reject the null hypothesis

Confidence interval for the test statistic between "0.5" and "2" was obtained for H(null)=0
```{r}
t.test(x1, x3, paired = FALSE, var.equal = FALSE)$conf
```

Since the interval does not include 0, We reject the null hypothesis

Confidence interval for the test statistic between "1" and "2" was obtained for H(null)=0
```{r}
t.test(x2, x3, paired = FALSE, var.equal = FALSE)$conf
```

Since the interval does not include 0, We reject the null hypothesis